### 2007-01-11 Documentation/part1.tex
*** empty log message ***

\begin{table}[tbp]
\begin{center}
\begin{tabular}{llp{7.5cm}c}
\hline
Experiment & Filename & Short description &  Ref. \\
\hline 
\multicolumn{4}{l}{\underline{Conventional beams:}} \\
MINOS & {\tt MINOS.glb} & MINOS exp., 5~yr running time & \cite{Huber:2004ug}\\
OPERA & {\tt OPERA.glb} & OPERA exp., 5~yr running time & \cite{Huber:2004ug}\\
ICARUS & {\tt ICARUS.glb} & ICARUS exp., 5~yr running time & \cite{Huber:2004ug}\\[0.1cm]

\multicolumn{4}{l}{\underline{First-generation superbeams:}} \\
T2K & {\tt JHFSKnew.glb} & J-PARC to Super-K, 5~yr $\nu$-running &  \cite{Huber:2002rs} \\
 & {\tt JHFSKantinew.glb} & J-PARC to Super-K, 5~yr $\bar{\nu}$-running &  \cite{Huber:2002rs} \\
 & {\tt JHFSKcomb.glb} & Same, but 1.25~yr $\nu$- and 3.75~yr $\bar{\nu}$-running &  \cite{Huber:2002rs} \\[0.1cm]
NO$\nu$A & {\tt NUMI9.glb} & NuMI OA $9 \, \mathrm{km}/712 \, \mathrm{km}$, 5~yr $\nu$-running & \cite{Huber:2002rs} \\
& {\tt NUMI9anti.glb} & NuMI OA $9 \, \mathrm{km}/712 \, \mathrm{km}$, 5~yr $\bar{\nu}$-running & \cite{Huber:2002rs} \\
& {\tt NUMI9comb.glb} & NuMI OA $9 \, \mathrm{km}/712 \, \mathrm{km}$, 1.43~yr $\nu$- and 3.57~yr $\bar{\nu}$-running & \cite{Huber:2002rs} \\
& {\tt NUMI12.glb} & NuMI OA $12 \, \mathrm{km}/712 \, \mathrm{km}$, 5~yr $\nu$-running & \cite{Huber:2002rs} \\
& {\tt NUMI12anti.glb} & NuMI OA $12 \, \mathrm{km}/712 \, \mathrm{km}$, 5~yr $\bar{\nu}$-running & \cite{Huber:2002rs} \\
& {\tt NUMI12comb.glb} & NuMI OA $12 \, \mathrm{km}/712 \, \mathrm{km}$, 1.43~yr $\nu$- and 3.57~yr $\bar{\nu}$-running & \cite{Huber:2002rs} \\[0.1cm]

\multicolumn{4}{l}{\underline{Superbeam upgrade:}} \\
J-PARC-HK & {\tt JHFHKAll.glb} & J-PARC to Hyper-K, 2~yr $\nu$- and 6~yr $\bar{\nu}$-running &  \cite{Huber:2002mx} \\[0.1cm]

\multicolumn{4}{l}{\underline{Neutrino factories:}} \\
\NuFactI\ & {\tt NuFact1.glb} & Initial stage NF, 2$\times$2.5~yr running time (each pol.), $m_{\mathrm{Det}} = 10 \, \mathrm{kt}$,
$P_{\mathrm{Tg}} \simeq 0.75 \, \mathrm{MW}$ & \cite{Huber:2002mx} \\
\NuFactII\  & {\tt NuFact2.glb} & Advanced stage NF, 2$\times$4~yr running time (each pol.), $m_{\mathrm{Det}} = 50 \, \mathrm{kt}$,
$P_{\mathrm{Tg}} \simeq  4 \, \mathrm{MW}$ & \cite{Huber:2002mx} \\[0.1cm]

\multicolumn{4}{l}{\underline{Reactor experiments:}} \\
\ReactorI\ & {\tt Reactor1.glb} & Small reactor exp., $\mathcal{L} = 400 \, \mathrm{t} \, \mathrm{GW} \, \mathrm{yr}$ & \cite{Huber:2003pm} \\
\ReactorII\ & {\tt Reactor2.glb} & Large reactor exp., $\mathcal{L} = 8\, 000 \, \mathrm{t} \, \mathrm{GW} \, \mathrm{yr}$ & \cite{Huber:2003pm} \\[0.1cm]

\underline{$\beta$-Beams:} & \multicolumn{3}{l}{In preparation} \\[0.1cm]
\hline
\end{tabular}
\end{center}
\mycaption{\label{tab:experiments} \index{norm}{Experiment files (table)}
\index{norm}{glb files@{\tt glb}-files} 
TO BE UPDATED BY MR; POSSIBLY MORE DETAILED DESCRIPTION IN APPENDIX [WW]. Pre-defined experiment prototypes, their filenames (to be used in \GLB{InitExperiment}), their short descriptions, and the references in which they are originally used and discussed (except from minor modifications, such as a
different implementation of the energy threshold function). Note that
some of these experiments are outdated in terms of integrated luminosities,
baseline, fluxes, efficiencies, or other factors. In any case these file are installed along with \GLOBES.}
\end{table}

>>>>

\begin{table}[tbp]
\begin{center}
\begin{tabular}{llp{7.5cm}c}
\hline
Experiment & Filename & Short description &  Ref. \\[0.2cm]
\hline 
\multicolumn{4}{l}{\underline{Superbeam experiments:}} \\[0.2cm]

T2K & {\tt T2K.glb} & J-PARC to Super-K, 2~yr $\nu$- and 6~yr 
$\bar{\nu}$-running &  \cite{Itow:2001ee,Huber:2002mx} \\[0.2cm]

T2HK & {\tt T2HK.glb} & J-PARC to Hyper-K, 4~yr $\nu$- and 4~yr 
$\bar{\nu}$-running (T2K upgrade) &  \cite{Itow:2001ee,Huber:2002mx} \\[0.2cm]

NO$\nu$A & {\tt NOvA.glb} & FermiLab NuMI beamline off-axis, 3~yr $\nu$- and 
3~yr $\bar{\nu}$-running  & \cite{Ambats:2004js,Yang_2004} \\[0.2cm]

SPL & {\tt SPL.glb} & CERN to Fr\'{e}jus, 2~yr $\nu$- and 8~yr 
$\bar{\nu}$-running & \cite{Campagne:2006yx,Campagne:2004wt,Mezzetto:2003mm} \\[0.2cm]

\multicolumn{4}{l}{\underline{Reactor experiments:}} \\[0.2cm]

{\sc Reactor-I} & {\tt Reactor1.glb} & Small reactor exp., 
$\mathcal{L} = 400 \, \mathrm{t} \, \mathrm{GW} \, \mathrm{yr}$
& \cite{Huber:2003pm} \\[0.2cm]

{\sc Reactor-II} & {\tt Reactor2.glb} & Large reactor exp., 
$\mathcal{L} = 8\, 000 \, \mathrm{t} \, \mathrm{GW} \, \mathrm{yr}$ 
& \cite{Huber:2003pm} \\[0.2cm]

Double{\sc Chooz} & {\tt D-Chooz\_near.glb} & DoubleCHOOZ near 
detector, 5 years data taking & \cite{Huber:2006vr} \\ 
 & {\tt D-Chooz\_far.glb} & DoubleCHOOZ near detector, 5 years data taking & \\[0.2cm]

\multicolumn{4}{l}{\underline{$\beta$-Beams:}} \\[0.2cm]

low $\gamma$ & {\tt BB\_100.glb} & $\gamma=100$ CERN to Fr\'{e}jus baseline 
scenario, 4~yr $\nu$- and 4~yr $\bar{\nu}$-running & \cite{Campagne:2006yx} \\[0.2cm]

medium $\gamma$ & {\tt BB\_350.glb} & $\gamma=350$ frogreen field scenario, 4~yr $\nu$- and
4~yr $\bar{\nu}$-running & \cite{Burguet-Castell:2005pa} \\[0.2cm]

Variable & {\tt BBvar\_WC.glb} & Variable $\beta$-beam, 4~yr $\nu$- and 
4~yr $\bar{\nu}$-running, {\sf AEDL}-Variables {\tt gammafactor}, 
{\tt EXP\_FACTOR} and {\tt baselinefactor}, 500~kt WC detector & \cite{Huber:2005jk} \\[0.2cm]

	& {\tt BBvar\_TASD.glb} & like {\tt BBvar\_WC.glb} but with a 50~kt TASD detector  
& \cite{Huber:2005jk} \\[0.2cm]

\multicolumn{4}{l}{\underline{Neutrino factories:}} \\[0.2cm]

Standard & {\tt NFstandard.glb} & Standard neutrino factory, 
4~yr $\nu$- and 4~yr $\bar{\nu}$-running & \cite{Huber:2002mx} \\[0.2cm]

Variable  & {\tt NFvar.glb} & Variable neutrino factory, 4~yr 
$\nu$- and 4~yr $\bar{\nu}$-running, {\sf AEDL}-Variables {\tt emax} and {\tt BASELINE}, disappearance channels
{\em without} CID & \cite{Huber:2002mx,Huber:2006wb}  \\[0.2cm]

Gold + Silver & {\tt NF\_Goldsilver.glb} & as {\tt NFvar.glb} 
plus 5~kt ECC detector for Silver Channel
measurement & \cite{Huber:2002mx,Huber:2006wb,Autiero:2003fu} \\[0.2cm]

Hybrid detector & {\tt NF\_hR\_lT.glb} & like {\tt NFvar.glb} 
with lower threshold and higher energy resolution & \cite{Huber:2002mx,Huber:2006wb} \\[0.2cm]

\hline
\end{tabular}
\end{center}
\mycaption{\label{tab:experiments} \index{norm}{Experiment files (table)}
\index{norm}{glb files@{\tt glb}-files} 
Pre-defined experiment prototypes, their filenames (to be used in \GLB{InitExperiment}), 
their short descriptions, and the references in which they are originally used and 
discussed (except from minor modifications, such as a different implementation of 
the energy threshold function). Note that some of these experiments are outdated 
in terms of integrated luminosities, baseline, fluxes, efficiencies, or other factors. 
In any case these file are installed along with \GLOBES.}
\end{table}
